### 2020-12-21 paper/localpsf.tex
improved point picking algorithm box

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P \subset \Omega_I$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ randomly from $P$, one at a time. If $p$ is sufficiently far from all of the previously chosen points, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until it is no longer possible to pick a point from $P$ that is sufficiently far from the points in $S_b$. 
%This is detailed in Algorithm \ref{alg:point_choice}.

We repeat the process to construct several batches of points $S_1, S_2, \dots$, until the total number of sample points exceeds a desired threshold. We write $S = S_1 \cup \dots$ to denote the set of sample points from all batches. In our implementation, the set of candidate points $P$ is the set of all Lagrange nodes for the finite element basis functions $\phi_i$ used to discretize the problem, minus all of the Lagrange nodes that are in $\Omega_B$, minus all points in previously chosen batches.

@@

%		\If{$\text{point\_is\_acceptable}(p, S_b)$}{
		\If{$E_p \cap E_q \neq \{\}$ for all $q \in S_b$}{

>>>>

We select a batch of sample points, $S_b$, randomly from a finite set of candidate points $P$. Starting from an empty set, we build $S_b$ by choosing candidate points $p$ from $P$, one at a time. The current candidate point, $p$, is the point in $P$ that is the farthest away from all points in previous sample point baches. That is, the minimizer of the following optimization problem:
\begin{equation*}
\min_{p \in P} \max_{x \in S_1 \cup \dots \cup S_{b-1}} \|p - x\|
\end{equation*}
After we choose the candidate $p$, we remove $p$ from $P$.
If $p$ is sufficiently far from all of the previously chosen points in the current batch, in the sense that $E_p \cap E_q = \{\}$ for all $q \in S_b$, and if $p$ is sufficiently far from the boundary, in the sense that $E_p \cap \partial \Omega = \{\}$, then we add $p$ to $S_b$. Otherwise we discard $p$. This process repeats until it is no longer possible to pick a point from $P$ that is sufficiently far from the points in $S_b$. 
%This is detailed in Algorithm \ref{alg:point_choice}.

We repeat the process to construct several batches of points $S_1, S_2, \dots$, until the total number of sample points exceeds a desired threshold. In our implementation, the set of candidate points $P$ is the set of all Lagrange nodes for the finite element basis functions $\phi_i$ used to discretize the problem, minus all points in previously chosen batches.

@@

%		\If{$\text{point\_is\_acceptable}(p, S_b)$}{
		\If{$E_p \cap E_q \neq \{\}$ for all $q \in S_b$ and $E_p \cap \partial \Omega = \{\}$}{
